Marginally-Stable Thermal Equilibria of Rayleigh-Bénard Convection

### 2021-04-15 publication_materials/ms_rbc.tex

\begin{abstract}
Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive -- particularly in the large Rayleigh number regime.
In this investigation, we derive and solve a quasilinear form of the Boussinesq Rayleigh-B\'enard equations. 
Eigenfunction amplitudes are obtained by requiring marginal-stability. We obtain symmetric thermally-equilibrated solutions and analyze their properties. 
Solutions to the quasilinear problem differ from statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulation data, having thinner boundary layers and larger Nusselt numbers $\Nu$ which scale like $\Nu \sim Ra^{1/3}$. 
We initialize 2-dimensional simulations with solutions to the quasilinear problem; they do not undergo a convective transient period and are kinetically exaggerated.
\end{abstract}

>>>>

\begin{abstract}
Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive---particularly in the large Rayleigh number regime.
In this investigation, we derive and solve a quasilinear form of the Rayleigh-Benard problem by representing the perturbations in terms of marginally stable eigenmodes.
The amplitude of each eigenmode is determined by requiring that the background state maintains marginal stability.
The background temperature profile evolves due to the advective flux of each eigenmode, as well as diffusion.
The entire calculation is one-dimensional, and can be run on a workstation.
We find the background temperature field evolves to an equilibrium state, where the advective flux from the marginally-stable eigenmodes and the diffusive flux sum to a constant.
These marginally-stable thermal equilibria are exact solutions of the quasilinear equations.
The mean temperature profile has thinner boundary layers and larger Nusselt numbers than thermally-equilibrated 2D and 3D simulations of the full nonlinear equations.
We find the Nusselt number scales like $\Nu \sim Ra^{1/3}$.
When initializing a 2D simulation with a marginally-stable thermal equilibrium, we find the simulation does not exhibit the initial burst of turbulence typical of simulations initialized with the conductive background state plus noise.
Although the $\Nu$ quickly equilibrates in these simulations, the kinetic energy evolves on a viscous timescale as domain-filling flywheel flows viscously attenuate.
\end{abstract}
